### 2015-04-27 paper/preamble.tex
Move figure commands out of the preamble to allow externalized generation

% Speed up pgfplots/tikz figure generation by caching results.
% LyX needs to be configured per user;
% In LyX Preferences, File Handling, Converters:
% For LaTeX (pdflatex) -> PDF (pdflatex) set the Converted field to:
% pdflatex -shell-escape $$i
% (Adding  -shell-escape is what is important.)
\usepgfplotslibrary{external}
% When using LyX, the command is executed in a temporary working directory; can't use a folder prefix.
\tikzexternalize[prefix=.generated.]
% Use to remake all or remake a single figure.
%\tikzset{external/force remake}
%\tikzset{external/remake next}

\usepgfplotslibrary{groupplots}

\pgfplotsset{allDatasetsXbar/.style=
{
enlarge x limits=false,
bar width=6pt,
fill opacity=0.9,
xmin=0,
xmax=1,
xtick={0,.2,.4,.6,.8,1},
minor xtick={.1,.3,.5,.7,.9},
xminorgrids=true,
xmajorgrids=true,
ytick=data,
y dir=reverse,
yticklabel pos=right,
symbolic y coords={alexa.2014-09-01.random.10000-http,alexa.2014-09-01.random.10000-http-www,alexa.2014-09-01.random.10000-https,alexa.2014-09-01.random.10000-https-www,alexa.2014-09-01.top.10000-http,alexa.2014-09-01.top.10000-http-www,alexa.2014-09-01.top.10000-https,alexa.2014-09-01.top.10000-https-www,alexa.2014-09-01.top.dk.10000-http,alexa.2014-09-01.top.dk.10000-http-www,alexa.2014-09-01.top.dk.10000-https,alexa.2014-09-01.top.dk.10000-https-www,alexa.2014-09-01.top.se.10000-http,alexa.2014-09-01.top.se.10000-http-www,alexa.2014-09-01.top.se.10000-https,alexa.2014-09-01.top.se.10000-https-www,com.2014-08-29.random.10000-http,com.2014-08-29.random.10000-http-www,com.2014-08-29.random.10000-https,com.2014-08-29.random.10000-https-www,dk.2014-07-23.random.10000-http,dk.2014-07-23.random.10000-http-www,dk.2014-07-23.random.10000-https,dk.2014-07-23.random.10000-https-www,net.2014-08-29.random.10000-http,net.2014-08-29.random.10000-http-www,net.2014-08-29.random.10000-https,net.2014-08-29.random.10000-https-www,reach50.2014w35.se-http,reach50.2014w35.se-http-www,reach50.2014w35.se-https,reach50.2014w35.se-https-www,se.2014-07-10.random.100000-http,se.2014-07-10.random.100000-http-www,se.2014-07-10.random.100000-https,se.2014-07-10.random.100000-https-www,se.healthstatus.2013.counties-http,se.healthstatus.2013.counties-http-www,se.healthstatus.2013.counties-https,se.healthstatus.2013.counties-https-www,se.healthstatus.2013.domain-registrars-http,se.healthstatus.2013.domain-registrars-http-www,se.healthstatus.2013.domain-registrars-https,se.healthstatus.2013.domain-registrars-https-www,se.healthstatus.2013.financial-services-http,se.healthstatus.2013.financial-services-http-www,se.healthstatus.2013.financial-services-https,se.healthstatus.2013.financial-services-https-www,se.healthstatus.2013.gocs-http,se.healthstatus.2013.gocs-http-www,se.healthstatus.2013.gocs-https,se.healthstatus.2013.gocs-https-www,se.healthstatus.2013.higher-education-http,se.healthstatus.2013.higher-education-http-www,se.healthstatus.2013.higher-education-https,se.healthstatus.2013.higher-education-https-www,se.healthstatus.2013.isps-http,se.healthstatus.2013.isps-http-www,se.healthstatus.2013.isps-https,se.healthstatus.2013.isps-https-www,se.healthstatus.2013.media-http,se.healthstatus.2013.media-http-www,se.healthstatus.2013.media-https,se.healthstatus.2013.media-https-www,se.healthstatus.2013.municipalities-http,se.healthstatus.2013.municipalities-http-www,se.healthstatus.2013.municipalities-https,se.healthstatus.2013.municipalities-https-www,se.healthstatus.2013.public-authorities-http,se.healthstatus.2013.public-authorities-http-www,se.healthstatus.2013.public-authorities-https,se.healthstatus.2013.public-authorities-https-www},
legend image code/.code={%
\draw[#1] (0pt,-4pt) rectangle (8pt,4pt);
},
},
allDatasetsXbarFullPage/.style=
{
enlarge y limits=0.008,
width=.65\textwidth,
height=1.47\textwidth,
font=\small,
legend columns=-1,
legend style={at={(0.5,-16pt)},anchor=north}
},
allDatasetsXbarMiniResults/.style=
{
enlarge y limits=0.1,
width=.4\textwidth,
height=.325\textwidth,
font=\tiny,
legend columns=-1,
legend style={at={(0.5,-12pt)},anchor=north},
symbolic y coords={alexa.2014-09-01.top.10000-http-www,alexa.2014-09-01.top.10000-https-www,alexa.2014-09-01.top.se.10000-http-www,alexa.2014-09-01.top.se.10000-https-www,se.2014-07-10.random.100000-http-www,se.2014-07-10.random.100000-https-www,se.healthstatus.2013.municipalities-http-www,se.healthstatus.2013.municipalities-https-www,},
xticklabel style={
/pgf/number format/fixed,
/pgf/number format/fixed zerofill=false,
/pgf/number format/precision=1
},
title style={at={(.5,.95)}},
},
xticklabel style={
/pgf/number format/fixed,
/pgf/number format/fixed zerofill,
/pgf/number format/precision=2
},
yticklabel style={
/pgf/number format/fixed,
/pgf/number format/fixed zerofill,
/pgf/number format/precision=2
}
}
\pgfplotsset{allDatasetsStackedXbar/.style=
{
xbar stacked=plus,
},
}

\pgfplotsset{allDatasetsMultiXbar/.style=
{
xbar,
},
allDatasetsMultiXbarPart2/.style=
{
bar width=4pt,
% bar direction=y,
ymajorgrids=true,
major y grid style={loosely dashed},
},
}

\newcommand{\XBarPlotFromDataset}[5]{
	\addplot[
			fill=#4,#5
		]
		table[y=Dataset,x=#2]
		{#1};
	\addlegendentry{#3}
}

\pgfplotsset{datasetsCDF/.style=
{
xmin=0,
xmax=1,
ymin=0,
ymax=1,
grid=both,
xtick={0,.1,...,1.1},
ytick={0,.1,...,1.1},
enlargelimits=false,
% Marks 0% and 99%.
mark repeat=99,
% Using a custom position below.
% legend pos=south east,
legend style={
at={(.99,.01)},
anchor=south east,
cells={anchor=west},
},
},
datasetsCDFFullPage/.style=
{
width=\textwidth,
height=1.46\textwidth,
},
datasetsCDFMiniResults/.style=
{
width=.4\textwidth,
height=.325\textwidth,
font=\tiny,
xtick={0,.2,...,1.0},
ytick={0,.2,...,1.0},
minor xtick={0,.1,...,1.1},
minor ytick={0,.1,...,1.1},
xticklabel style={
/pgf/number format/fixed,
/pgf/number format/fixed zerofill=false,
/pgf/number format/precision=1
},
yticklabel style={
/pgf/number format/fixed,
/pgf/number format/fixed zerofill=false,
/pgf/number format/precision=1
},
title style={at={(.5,.95)}},
}
}

\pgfplotsset{datasetsOccurances/.style=
{
ymin=,
xmin=0.1,
xmax=100,
xtick={0.1,1,2,3,4,5,10,20,50,100},
minor xtick={6,7,8,9,30,40,60,70,80,90},
xticklabel={%
	\ifnum\ticknum=9%
		$100^+$%
	\else%
		\pgfmathfloatparsenumber{\tick}%
		\pgfmathfloatexp{\pgfmathresult}%
		\pgfmathprintnumber[fixed,precision=0]{\pgfmathresult}%
	\fi%
},
yticklabel style={
/pgf/number format/fixed,
/pgf/number format/fixed zerofill,
/pgf/number format/precision=2
},
% Marks 0.1.
mark repeat=1,
mark indices={1},
},
datasetsOccurancesMiniResults/.style=
{
width=.35\textwidth,
height=.325\textwidth,
font=\tiny,
xmax=15,
xtick={0.1,1,5,10,15},
ytick={0,.2,...,1.0},
minor xtick={2,3,4,6,7,8,9,11,12,13,14},
xticklabel={%
	\pgfmathfloatparsenumber{\tick}%
	% \pgfmathfloatexp{\pgfmathresult}%
	\pgfmathprintnumber[fixed,precision=0]{\pgfmathresult}%
},
minor ytick={0,.1,...,1.1},
yticklabel style={
/pgf/number format/fixed,
/pgf/number format/fixed zerofill=false,
/pgf/number format/precision=1
},
title style={at={(.5,.95)}},
},
}

\newcommand{\CDFPlotFromDataset}[3]{
	\addplot+[#3,solid,mark=*,every mark/.append style={#3,solid},]
		table[x=colnames,y=#2-http-www]
		{#1};
	\addlegendentry{#2-http-www}
	\addplot+[#3,dashed,mark=square*,every mark/.append style={#3,solid},]
		table[x=colnames,y=#2-https-www]
		{#1};
	\addlegendentry{#2-https-www}
}

\newcommand{\CDFPlotFromDefaultDatasets}[1]{
	\CDFPlotFromDataset{#1}{alexa.2014-09-01.top.10000}{red}
	\CDFPlotFromDataset{#1}{alexa.2014-09-01.top.se.10000}{blue}
	\CDFPlotFromDataset{#1}{se.2014-07-10.random.100000}{brown}
	\CDFPlotFromDataset{#1}{se.healthstatus.2013.municipalities}{violet}
	% \CDFPlotFromDataset{#1}{se.healthstatus.2013.media}{teal}
}

\newcommand{\CDFPlotFromDefaultDatasetsFile}[1]{
	\pgfplotstabletranspose[colnames from=Dataset]\tableTransposedDatasetsFromFile{#1}

	\CDFPlotFromDefaultDatasets{\tableTransposedDatasetsFromFile}
}

>>>>

\usepackage[pfx=.generated.]{jpfigurecommands}
